%-------------------------
% Resume in Latex
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{3.60004pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Juan Carlos Barrera} \\ \vspace{1pt}
    \small +61 0426 916 062 $|$
    \href{mailto:jcbp1999@gmail.com}{\underline{jcbp1999@gmail.com}} $|$
    \href{https://linkedin.com/in/juan-carlos-barrera-pinilla-16b13419b}{\underline{linkedin/juan-barrera}} $|$
    \href{https://github.com/Pakas342}{\underline{github/Pakas342}} $|$
    Sydney, Australia
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{Full-stack engineer with 4 years of production experience delivering end-to-end web applications across fintech and e-commerce domains. Specialises in Node.js/NextJS/Remix.js back-ends, Next.js/React front-ends, and PostgreSQL data layers, with hands-on work in OAuth 2.0 flows, API security (CORS, encryption, key management), and Swagger/OpenAPI documentation. Comfortable owning the full lifecycle from architecture through CI/CD deployment on GCP.}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Fullstack Developer}{Jul. 2024 -- Jun. 2025 $\cdot$ Dec. 2025 -- Present}
      {AdviceFlow}{Lisbon, Portugal (Remote)}
      \resumeItemListStart
        \resumeItem{Built and maintained RESTful APIs with NextJS integrating multiple third-party services}
        \resumeItem{Implemented OAuth 2.0, CORS policies, and payload encryption for financial data handling}
        \resumeItem{Modelled relational schemas with TypeORM on GCP-hosted PostgreSQL; applied query optimisation and caching to improve response times}
      \vspace{5pt}
      \resumeItemListEnd

    \resumeSubheading
      {Fullstack Developer}{Nov. 2024 -- Feb. 2026}
      {GeneralDev}{Denver, United States (Remote)}
      \resumeItemListStart
        \resumeItem{Built full-stack features connecting a Next.js/React front-end to Shopify APIs and custom Node.js back-end endpoints}
        \resumeItem{Developed AI features in Next.js including a RAG pipeline and chat interface backed by LLM APIs}
        \resumeItem{Built Python services with FastAPI and Flask to expose internal data-processing workflows as REST endpoints}
        \resumeItem{Configured CORS, API key management, and request encryption across service boundaries}
        \resumeItem{Managed CI/CD pipelines with GitHub Actions across staging and production environments}
      \vspace{5pt}
      \resumeItemListEnd

    \resumeSubheading
      {Back End Developer}{Mar. 2024 -- Jul. 2024}
      {Blackpeak}{Vancouver, Canada (Remote)}
      \resumeItemListStart
        \resumeItem{Built a headless storefront connecting a Webflow front-end to Shopify APIs through a Xano backend}
        \resumeItem{Built REST API endpoints with Node.js; integrated third-party OAuth providers and handled token lifecycle in a PostgreSQL session store}
      \vspace{5pt}
      \resumeItemListEnd

    \resumeSubheading
      {Back End Senior Developer}{Mar. 2022 -- Jan. 2024}
      {Castia (YC-backed)}{Bogot\'a, Colombia}
      \resumeItemListStart
        \resumeItem{Designed and owned the full API layer in Xano for a mobile app: endpoint structure, authentication with OAuth 2.0 and JWT, and encryption at rest and in transit}
        \resumeItem{Modelled the database schema and implemented all business logic in Xano, serving a no-code mobile frontend}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

\resumeSubheading
  {University of Sydney}{Sydney, Australia}
  {Master of Computer Science (Advanced Entry)}{2026 -- Present}
\vspace{-2pt}\resumeSubSubheading
  {Networks \& Distributed Systems / Algorithms \& Theory}{}
      \resumeItemListStart
        \resumeItem{Colfuturo Scholarship recipient, Colombian Government}
      \resumeItemListEnd

    \resumeSubheading
      {Sergio Arboleda University}{Bogot\'a, Colombia}
      {Bachelor of Finance and International Trade}{2017 -- 2021}
      \resumeItemListStart
        \resumeItem{Top 1\% nationally -- Saber Pro 2020 (230/300) $|$ Colciencias Research Scholarship $|$ GPA 4.40/5.00}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript, SQL, Python, C, Bash} \\
     \textbf{Front-End}{: Next.js, React, Tailwind CSS, HTML, CSS, RxJS} \\
     \textbf{Back-End}{: Node.js, NextJS, Remix.js, FastAPI, Flask, Xano} \\
     \textbf{Databases}{: PostgreSQL, TypeORM, CloudSQL, Supabase} \\
     \textbf{Security}{: OAuth 2.0, CORS, Encryption \& Decryption, Key Management} \\
\textbf{Cloud \& DevOps}{: GCP, Docker, GitHub Actions, Vercel} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
